The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-05-04 exp-resurgence.tex
Revise "A flavor of resurgence" a bit

It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and \cite[Chapter ??]{Arnold}. However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain. \textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a } 
%
%\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
%For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}. Let us assume $z \in (0, \infty)$ for the rest of the section. \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}

>>>>

It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \textcolor{orange}{[typically]} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula. Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~\textcolor{orange}{??}]{Arnold}. However, in the Airy--Lucas example, $f$ is not Morse unless $n=3$. Hence, we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain. \textcolor{orange}{[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]}
%
%\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
%For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}. Let us assume $z \in (0, \infty)$ for the rest of the section. \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
